Conjure: Summoning Proxies from Unused Address Space

### 2019-08-29 paper/paper.tex
Format
pass on discussion for ccs resubmission

\documentclass[sigconf]{acmart}
%\usepackage{usenix2019_v3}

@@

% to be able to draw some self-contained figs
\usepackage{tikz}
%\usepackage{parskip}
%\usepackage{mathptmx}\renewcommand{\ttdefault}{cmtt}
\usepackage{amsmath}
\usepackage{wasysym}
%\setlength{\parskip}{1pt} % 1ex plus 0.5ex minus 0.2ex}
%\setlength\parskip{1pt}
\usepackage{graphicx} % http://ctan.org/pkg/graphicx
\usepackage{booktabs} % http://ctan.org/pkg/booktabs
\usepackage{xparse}   % http://ctan.org/pkg/xparse%don't print date
\NewDocumentCommand{\rot}{O{45} O{1em} m}{\makebox[#2][l]{\rotatebox{#1}{#3}}}%
\include{figures}
\usepackage{subcaption}
\usepackage{cleveref}
\usepackage{microtype}
\SetExtraKerning{encoding=*,font=*}{\textemdash={120,120}} % Add space around emdashes
%\usepackage[font=small]{caption}
\microtypecontext{spacing=nonfrench}
%\usepackage{subcaption}
\usepackage{paralist}
\usepackage{xspace}
\usepackage{soul}
\newcommand{\note}[2]{\hl{[\textbf{#1:} #2]}\xspace}
\newcommand{\nikita}[1]{\note{nikita}{#1}}
\newcommand{\TODO}[1]{\hl{TODO: #1}\xspace}
\newcommand{\TK}{\hl{TK}\xspace}

@@

Obfuscated SSH~\cite{ossh} (OSSH) is a protocol that attempts to mask the Secure Shell
(SSH) protocol in a thin
layer of encryption. This makes it difficult for censors to identify using basic
packet filters, as there are no identifying headers or fields
to search for. Instead, Obfuscated SSH clients first send a 16-byte seed, which
is then used to derive a symmetric key that encrypts the rest of the
communication. While this can passively detected by censors (who can also
derive the key and de-obfuscate the protocol), the key derivation is deliberately
slowed by an iterated hash to make such identification
expensive (though not impossible) at high speeds.

Obfuscated SSH also does not protect against active probing, as the censor can
easily create their own connections and confirm the server is using the
protocol. Nonetheless, this protocol is still used in deployed censorship
circumvention systems~\cite{psiphon}, though has to deploy proxies at new IP
addresses when censors inevitably discover and block them.
Obfuscated SSH can also be used as a \scheme
application protocol, though we note it provides no active probing or passive
identification resistance. However, \scheme OSSH can still make it cheaper to
rotate to new IP addresses when proxies are found and blocked.

@@

We therefore attempt to mimic an existing \textbf{mask site} by relaying
traffic between the client and a selected mask website. To a censor, this site
will be indistinguishable from the legitimate mask site, making it difficult for
them to block without potentially blocking the actual site. TLS connections to the
application will terminate exactly as connections to the mask site would, with the
application acting as a transparent proxy between the client and mask site.
However, this leaves the application unable to introspect on the contents of the
TLS connection to the mask site, as it does not have the client-site shared
secrets, and it cannot overtly man-in-the-middle the connection before knowing
it is communicating with the legitimate client (and not the censor).

To covertly signal to the relaying application, the client changes the shared secret
it derives with the
mask site to something that the application can also derive. The client's first
\texttt{Application Data} packet is thus encrypted under a different secret than
the client/mask site secret. Specifically, the client uses the \textbf{seed}
sent during registration to derive the pre-master secret for the connection.
This is hashed along with the client and server randoms of the current (mask
site) TLS connection to obtain the master secret that determines
encryption/decryption/authentication keys.

@@

We implemented two of the applications in our client: Obfuscated SSH used by
Psiphon
(Section~\ref{sec:ossh}) and our Mask Site protocol
(Section~\ref{sec:mask-sites}). Our client signals which application it will use
in the registration tag. After registration, the client connects to the derived
phantom host address, and speaks the specified application protocol, which
tunnels a SOCKS connection between the client and Psiphon's backend servers,
which proxy the client's connections.

@@

\section{Discussion}

\subsection{Attacks and Defenses}
% 1 page
\label{sec:attacks}

There are many attacks a censor might attempt to either prevent phantom hosts from
being registered or used.

\paragraph{Blocking registration}
To make registration more difficult, censors could block TLS connections to all of the
limited decoys available in a deployment. Using TapDance's current deployment,
this would involve blocking over 1500 sites. We note that such an attack would
completely disable all existing Refraction Networking schemes, as none work
without being able to access legitimate decoys past the station. In \scheme,
this would only block new registrations, and would not impact users that
previously registered. Furthermore, registrations could also occur over email,
or over lower-bandwidth covert channels, such as port (or even IP) knocking past
the station, that would be more difficult for the censor to block.
%Cirripede previously used a registration protocol that sent covert information via initial
%sequence numbers in arbitrary TCP connections, though we note this solution
%generally requires clients to have root access to their device to control the
%initial sequence numbers. Since most mobile users do not have such control, we
%suggest other methods be used instead.

\paragraph{Scanning masked sites}
The censor could also attempt to fingerprint the masked site and compare it to a
suspected \scheme application. For instance, if a phantom host IP responds as
pretending to be \texttt{example.com}, the censor could scan or probe real instances
of \texttt{example.com} on different ports and see how it responds. Then, the
censor can probe the phantom host IP, and see if it responds similarly (e.g. with
the same set of open ports and payloads for certain kinds of probes). To defend
against this, we forward \emph{all} traffic destined to the phantom host to the
masked site, including ports that are not relevant to the proxy application
(e.g. non 443). This ensures that above the TCP layer, we appear to be the mask
site. However, there may be differences in TCP/IP implementations, for instance,
how IP IDs are incremented, or how TCP timestamps are incremented (or supported
at all) that may be different from the mask site. To combat this, we can filter
mask sites by those that have identical TCP/IP stacks to ours, as we use a
common Linux implementation. We also note that this attack only applies when we
use the mask site as an application, and that \scheme can support other
applications (e.g. obfsproxy, WebRTC, etc) that do not have this issue.

\paragraph{Website fingerprinting}
Website Fingerprinting~\cite{wang2014effective,hayes2016k,sirinam2018deep} (WF) uses the patterns of encrypted traffic to identify which website a client is connected to. WF uses a classifier to label the traffic as belonging to one of several known websites, or (in some variants), an unknown or background class. Though WF is commonly studied in the context of anonymous web browsing, a censor could also use WF to detect refraction networking by distinguishing known traffic patterns of legitimate uses of a decoy site from the traffic generated by refraction networking (unknown class). Alternatively, the censor could monitor all traffic for patterns consistent with a set of blocked websites.

\scheme applications that mimic specific websites (e.g., mask sites) are likewise susceptible to WF. To date, however, censors have not been observed using WF and similar techniques, possibly due to the significant uncertainty resulting from even the best algorithms: even a small false
positive rate means blocking mostly legitimate connections (due to the base rate
of normal traffic), and false negatives could allow clients to retry until they
gain access.

More importantly, \scheme applications offer great flexibility in deploying traffic analysis defenses; for example, traffic shaping strategies such as implemented in Slitheen~\cite{slitheen16} could be easily employed in \scheme. Furthermore,
\scheme applications are not limited to mimicking websites, and can support
any (or even a combination of) protocols. Finally, if encrypted SNI can be used (\cref{esni}), the censor would not be able to build up a traffic profile of a legitimate site since its identity would be encrypted.

\paragraph{ICMP}
Censors can use ping or traceroute utilities (via ICMP) to probe potential phantom
hosts. Because there is (usually) no host at the phantom host address, these
probes will timeout and produce no response. They might also produce
``Destination Unreachable'' responses from routers depending on how they are
configured. We performed a scan of 10~million IPv6 addresses in a routable /32
prefix to see if it is common to respond with such tell-tale ICMP messages for
unused messages. We found only 0.016\% of addresses responded with any ICMP
messages (mainly ``Time Exceeded'' and ``Destination Unreachable'').

>>>>

\documentclass[sigconf,anonymous]{acmart}
%\usepackage{usenix2019_v3}

@@

% to be able to draw some self-contained figs
\usepackage{tikz}
%\usepackage{parskip}
%\usepackage{mathptmx}\renewcommand{\ttdefault}{cmtt}
\usepackage{amsmath}
\usepackage{wasysym}
%\setlength{\parskip}{1pt} % 1ex plus 0.5ex minus 0.2ex}
%\setlength\parskip{1pt}
\usepackage{graphicx} % http://ctan.org/pkg/graphicx
\usepackage{booktabs} % http://ctan.org/pkg/booktabs
\usepackage{xparse}   % http://ctan.org/pkg/xparse%don't print date
\NewDocumentCommand{\rot}{O{45} O{1em} m}{\makebox[#2][l]{\rotatebox{#1}{#3}}}%
\include{figures}
\usepackage{subcaption}
\usepackage{cleveref}
\usepackage{microtype}
\SetExtraKerning{encoding=*,font=*}{\textemdash={120,120}} % Add space around emdashes
\usepackage[font=small]{caption}
\microtypecontext{spacing=nonfrench}
%\usepackage{subcaption}
\usepackage{paralist}
\usepackage{xspace}
\usepackage{soul}
\newcommand{\note}[2]{\hl{[\textbf{#1:} #2]}\xspace}
\newcommand{\nikita}[1]{\note{nikita}{#1}}
\newcommand{\TODO}[1]{\hl{TODO: #1}\xspace}
\newcommand{\TK}{\hl{TK}\xspace}

@@

Obfuscated SSH~\cite{ossh} (OSSH) is a protocol that attempts to mask the Secure Shell
(SSH) protocol in a thin
layer of encryption. This makes it difficult for censors to identify using basic
packet filters, as there are no identifying headers or fields
to search for. Instead, Obfuscated SSH clients first send a 16-byte random seed, which
is used to derive a symmetric key that encrypts the rest of the
communication. Early versions of OSSH were passively detectable by censors, who
can observe the random seed and derive the key, allowing them to de-obfuscate the protocol.
These versions also did
not protect against active probing attacks, as a censor can easily create their
own connections to confirm if a server supports the protocol.

More recent versions of OSSH, such as those used by Psiphon~\cite{psiphon}, mix a secret
value into the key derivation, thwarting the naive passive detection/decryption
attack. The secret is distributed out-of-band along with the proxy's address,
and is unknown to a passive or active-probing censor. If a client connects and cannot
demonstrate knowledge of
the secret, the OSSH server does not respond, making it more difficult for
censors to discover OSSH servers via active probing attacks.

%While this can passively detected by censors (who can also
%derive the key and de-obfuscate the protocol), the key derivation is deliberately
%slowed by an iterated hash to make such identification
%expensive (though not impossible) at high speeds.
%
%
%% This is wrong...it actually does protect against active probing
%Obfuscated SSH also does not protect against active probing, as the censor can
%easily create their own connections and confirm the server is using the
%protocol. Nonetheless, this protocol is still used in deployed censorship
%circumvention systems~\cite{psiphon}, though has to deploy proxies at new IP
%addresses when censors inevitably discover and block them.
%Obfuscated SSH can also be used as a \scheme
%application protocol, though we note it provides no active probing or passive
%identification resistance. However, \scheme OSSH can still make it cheaper to
%rotate to new IP addresses when proxies are found and blocked.

@@

We therefore attempt to mimic an existing \textbf{mask site} by relaying
traffic between the client and a selected mask website. To a censor, this site
will be indistinguishable from the actual site, making it difficult for
them to block without potentially blocking the real site. TLS connections to the
application will terminate exactly as connections to the mask site would, with the
application acting as a transparent TCP-layer proxy between the client and mask site.
However, this leaves the application unable to introspect on the contents of the
TLS connection to the mask site, as it does not have the client-site shared
secrets, and it cannot overtly man-in-the-middle the connection before knowing
it is communicating with the legitimate client (and not the censor).

To covertly signal to the relaying application, the client changes the shared secret
it derives with the
mask site to something that the application can also derive. The client's first
\texttt{Application Data} packet is thus encrypted under a different secret than
the client/mask site secret. Specifically, the client uses the \textbf{seed}
sent during registration to derive the pre-master secret for the connection.
The new pre-master secret is hashed along with the client and server randoms of the current
(mask site) TLS connection to obtain the master secret that determines
encryption/decryption/authentication keys.

@@

We implemented two of the applications in our client: Obfuscated SSH used by
Psiphon
(Section~\ref{sec:ossh}) and our Mask Site protocol
(Section~\ref{sec:mask-sites}). Our client signals which application it will use
in the registration tag. The client also sends a flag that indicates if the
client supports IPv6, to allow IPv4-only clients to only derive IPv4 phantom
hosts.
After registration, the client connects to the derived
phantom host address, and speaks the specified application protocol, which
tunnels a SOCKS connection between the client and Psiphon's backend servers,
which proxy the client's connections.

@@

%\section{Discussion}

\section{Attacks and Defenses}
% 1 page
\label{sec:attacks}

In this section, we discuss several attacks a censor might attempt to either
block phantom hosts from being registered or used.

\subsection{Probing phantom hosts}
% censors could actively scan phantom hosts...we review how this works for obfs4, OSSH, masked sites individually
Censors may attempt to actively probe suspected phantom hosts to determine if
they are proxies or real hosts. China has been observed using exactly this technique to
discover existing proxies and Tor bridge
nodes~\cite{tor-bridge-blocking-blog,active-probe,ensafi-tor,china-blocking-tor}.
In response to China's active probing, Tor and other circumvention tool developers have developed
\emph{probe-resistant} protocols, such as \texttt{obfs4}~\cite{obfs4}, Obfuscated SSH
(OSSH)~\cite{ossh}, and Shadowsocks~\cite{shadowsocks}. Each of these protocols
require the client to know a special secret distributed alongside the original
proxy address. Without knowledge of this secret, active-probing censors will not
receive any response from these hosts, making it difficult for censors to tell if
a server is a proxy or a non-responsive legitimate host.

\paragraph{Obfuscated SSH} Modern OSSH protocols are intended to be
probe-resistant. Censors that attempt to probe suspected OSSH servers without
knowledge of the secret receive no data response, making it difficult to
distinguish them from other non-responsive hosts. To confirm this, we use
ZMap~\cite{zmap} to scan over 1 billion random IP/port combinations, and sent 25
random bytes (corresponding to the OSSH handshake) to the approximately 800,000
servers that responded. We expect very few of these to actually be OSSH
servers as they are simply random servers on random TCP ports.
However, over 99.4\% of them did not respond with any data, behavior mirrored by
OSSH servers.
Furthermore, 7.42\% of servers closed the connection with a TCP RST
after we send our random data, a response we also see with OSSH. While there may
be other ways to differentiate OSSH servers from others online, our tests
suggest censors could face steep false-positive rates in identifying OSSH
servers with active probing.

%TODO: how many servers in zmap look like OSSH? e.g. we send them 23 random
%bytes and then they don't respond with data. 99.46% (793789 out of 798032)
% If we send 25 bytes (~OSSH handshake size...), OSSH server responds with RST.
% zmap: 28.42% respond with RST within 4 secs. Only 7.49% within

\paragraph{\texttt{obfs4}}
Unlike previous versions of obfsproxy, the \texttt{obfs4} protocol is designed to
be resistant to active probing
attacks, requiring the client prove knowledge of a secret before the server will
respond. We verified that naive active probing attacks (where we attempt to
connect to an \texttt{obfs4} server without knowledge of the secret and see if
it provides proxy access) do not work
against \texttt{obfs4}. In addition, although China is effective at blocking
\texttt{obfs3}, the more recent probe-resistant \texttt{obfs4} remains a viable
proxy in the country

\paragraph{Mask sites}
The censor could also attempt to fingerprint a masked site and compare it to a
suspected \scheme application. For instance, if a phantom host IP responds to a
censors' probes
pretending to be \texttt{example.com}, the censor could probe real instances
of \texttt{example.com} on different ports and see how it responds. Then, the
censor can probe the phantom host IP, and see if it responds similarly (e.g. with
the same set of open ports and payloads for certain kinds of probes). To defend
against this, we forward \emph{all} traffic destined to the phantom host to the
masked site, including ports that are not relevant to the proxy application
(e.g. non 443). This ensures that above the TCP layer, we appear to be the mask
site. However, there may be differences in TCP/IP implementations, for instance,
how IP IDs are incremented, or how TCP timestamps are incremented (or supported
at all) that may be different from the mask site. To combat this, we can filter
mask sites by those that have identical TCP/IP stacks to ours, as we use a
common Linux implementation. We also note that this attack only applies when we
use the mask site as an application, and that \scheme can support other
applications (e.g. obfsproxy, WebRTC, etc) that do not have this issue.

We acknowledge that perfect mimicry of the real site is likely infeasible:
Houmansadr et al.~\cite{houmansadr-parrot} demonstrated the difficulty in fully
mimicking known applications, showing that staying fully-feature compatible is
an expensive and potentially intractable problem for circumvention systems.
However, their study focuses on \emph{application-specific} mimicry, used by
circumvention tools like CensorSpoofer, StegoTorus, and Skypemorph. These tools
generally attempt to mimic a specific protocol used by a complex application
such as Skype,
where only one or a handful of official popular clients are used. Houmansadr et
al.~\cite{houmansadr-parrot} show that such mimicry is difficult in practice due
to the complexity and opaqueness of specifications, side protocols that
applications may use, and intra- and inter-dependence on connections and other
protocols.

In contrast, mask sites have
the advantage that we can mimic any sites from a large set of heterogeneous real
websites, making it harder for a censor to fully fingerprint and characterize
\emph{all} potential mask sites. As websites may themselves use distributed
or heterogeneous server implementations, it could be more difficult for a
censor to block all mask site application use.
Nonetheless, it is still possible for censors to
use active probing attacks to detect either protocol feature, payload size, or
timing differences between mask sites and the real sites they attempt to mimic.

%This general issue remains an open problem in censorship circumvention; however,
%if solved, \scheme can use it to thwart active probing attacks in a useable
% and flexible system.

\subsection{Passive identification}
Censors might also attempt to use passive methods to distinguish and block communication
with registration decoys or phantom hosts. For example, 
Website Fingerprinting~\cite{wang2014effective,hayes2016k,sirinam2018deep} (WF)
uses the patterns of encrypted traffic to identify which website a client is
connected to. WF uses a classifier to label the traffic as belonging to one of
several known websites, or (in some variants), an unknown or background class.
Though WF is commonly studied in the context of anonymous web browsing, a censor
could also use WF to detect \scheme applications by distinguishing known traffic
patterns of legitimate website use from traffic generated by \scheme (unknown
class). Alternatively, the censor could monitor traffic for patterns consistent
with tunneled access to a set of blocked websites.

Wang et al.~\cite{wang2015seeing} demonstrated several effective classifiers
that can passively distinguish normal traffic from obfuscated circumvention
protocols including \texttt{obfs3}, \texttt{obfs4}, Format-transforming
encryption~\cite{fte}, and meek~\cite{meek}. However, despite the low false
positive rate of these classifiers, Wang et~al.~\cite{wang2015seeing} caution
that the base rate of normal traffic compared to obfuscated traffic would force
censors that employ such attacks to suffer significant collateral damage in
degrading performance and reliability of legitimate traffic.
Indeed, to date, censors have not been observed using WF or other
passive techniques, possibly due to the inaccuracy of these identification
techniques in practice. Even small false positive rates means blocking mostly legitimate
connections, and false negatives could allow clients to retry until they gain
access.

More importantly, \scheme applications offer great flexibility in deploying
traffic analysis defenses; for example, traffic shaping strategies such as
implemented in Slitheen~\cite{slitheen16} could be easily employed in \scheme.
\scheme clients could also choose from a large set of potential applications,
forcing censors to have to block access to all of them to block use.
%Furthermore, \scheme applications are not limited to mimicking websites, and can
%support any (or even a combination of) protocols. Finally, if encrypted SNI can
%be used (\cref{esni}), the censor would not be able to build up a traffic
%profile of a legitimate site since its identity would be encrypted.

\subsection{Blocking registration}
To make registration more difficult, censors could block TLS connections to all of the
limited decoys available in a deployment. Using TapDance's current deployment,
this would involve blocking over 1500 sites. We note that such an attack would
completely disable all existing Refraction Networking schemes, as none work
without being able to access legitimate decoys past the station. In \scheme,
this would only block new registrations, and would not impact users that
previously registered. Furthermore, registrations could also occur over email,
or over lower-bandwidth covert channels, such as port (or even IP) knocking past
the station, that would be more difficult for the censor to block.
%Cirripede previously used a registration protocol that sent covert information via initial
%sequence numbers in arbitrary TCP connections, though we note this solution
%generally requires clients to have root access to their device to control the
%initial sequence numbers. Since most mobile users do not have such control, we
%suggest other methods be used instead.

\subsection{ICMP}
Censors can use ping or traceroute utilities (via ICMP) to probe potential phantom
hosts. Because there is (usually) no host at the phantom host address, these
probes will timeout and produce no response. They might also produce
``Destination Unreachable'' responses from routers depending on how they are
configured. We performed a scan of 10~million IPv6 addresses in a routable /32
prefix to see if it is common to respond with such tell-tale ICMP messages for
unused messages. We found only 0.016\% of addresses responded with any ICMP
messages (mainly ``Time Exceeded'' and ``Destination Unreachable'').
